Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2018-08-23 workflow/workflow.Rmd
Added back Kelly's paragraph

>>>>

We are also developing a downstream method to identify genes that are DE either within or between lineages inferred from Slingshot. Whereas the GAM presented here can only identify dynamic genes within a single lineage, many researchers may be interested in finding genes that exhibit different expression patterns between lineages or identifying those genes which differentiate the earliest. For questions such as these, we are developing new, spline- and negative binomial-based methods for comparing gene dynamics between branching trajectories.
